The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2024-02-29 analysis/paper/paper.qmd
Update author information in YAML header

---
title: "The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach"
author:
  - Claudiu Forgaci:
      correspondence: "yes"
      email: C.Forgaci@tudelft.nl
      orcid: 0000-0003-3218-5102
      institute: tud
institute:
  - tud:
      name: Delft University of Technology
      address: Julianalaan 134, 2628 BL, Delft, Zuid-Holland, The Netherlands
title-block-published: "Last updated"  
date: now
date-format: long
format: pdf
  # docx:
  #   reference-doc: "../templates/template.docx" # Insert path for the DOCX file
  # pdf:
  #   template: "../templates/plos_latex_template.tex"
execute:
  echo: false
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  This paper aims to describe the legacy of the European post-Master of Urbanism 
  (EMU) that ran between 2005 and 2021 at TU Delft. To that end, it reports on the
  analysis of the graduation theses produced over the duration of the program.
  The text mining approach allows for a close scrutiny of the latent thematic patterns, 
  and evolutions thereof, found in the full texts of the theses. Results reveal 5 topics
  that are to a large extent consistent with the set-up of the program in two thematic 
  semesters at TU Delft and three possible exchange semester locations, each characterised 
  by a specific approach. The paper discusses the relevance of the findings for the
  state of the profession and education in the field. Set up as a research
  compendium accompanied by a published FAIR dataset and an interactive dashboard, 
  the research is fully reproudcible and enables further analysis. 
keywords: |
  urbanism; education; post-master; text mining; topic modeling
highlights: |
  These are the highlights. 
---

>>>>

---
title: "The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach"
author:
  - name: Claudiu Forgaci
    correspondence: "yes"
    email: C.Forgaci@tudelft.nl
    orcid: 0000-0003-3218-5102
    affiliations: 
      - ref: tud
affiliations:
  - id: tud
    name: Delft University of Technology
    address: Julianalaan 134, 2628 BL, Delft, Zuid-Holland, The Netherlands
title-block-published: "Last updated"  
date: now
date-format: long
format: pdf
  # docx:
  #   reference-doc: "../templates/template.docx" # Insert path for the DOCX file
  # pdf:
  #   template: "../templates/plos_latex_template.tex"
execute:
  echo: false
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  This paper aims to describe the legacy of the European post-Master of Urbanism 
  (EMU) that ran between 2005 and 2021 at TU Delft. To that end, it reports on the
  analysis of the graduation theses produced over the duration of the program.
  The text mining approach allows for a close scrutiny of the latent thematic patterns, 
  and evolutions thereof, found in the full texts of the theses. Results reveal 5 topics
  that are to a large extent consistent with the set-up of the program in two thematic 
  semesters at TU Delft and three possible exchange semester locations, each characterised 
  by a specific approach. The paper discusses the relevance of the findings for the
  state of the profession and education in the field. Set up as a research
  compendium accompanied by a published FAIR dataset and an interactive dashboard, 
  the research is fully reproudcible and enables further analysis. 
keywords: |
  urbanism; education; post-master; text mining; topic modeling
highlights: |
  These are the highlights. 
---
